How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-21 analysis/paper/paper.Rmd
add citation to Spearman

```{r show-plot-feedback-correlations, fig.cap = "Correlations among feedback items with Likert scale responses. The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive). Correlations were computed using Spearman's method."}
include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))
```

>>>>

(ref:correlation-caption) Correlations among feedback items with Likert scale responses. The size of the dot indicates the magnitude of the correlation, and the colour indicates the direction (red is negative, blue is positive). Correlations were computed using Spearman's [-@spearman1904proof] method.

```{r show-plot-feedback-correlations, fig.cap = "(ref:correlation-caption)"}
include_graphics(here::here("analysis/figures/feedback_likert_corr.png"))
```
